An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-13 poly-embed-journal/poly-embed-journal.tex
pass over a bunch of spots

\newcommand{\Li}[1]{L_{(#1)}}
\newcommand{\Ri}[1]{\R^{(#1)}}
\newcommand{\elli}[1]{\ell^{(#1)}}

@@

%% intuition for the relationship between polyhedral surrogates and discrete target losses
Underpinning our results are several observations, outlined in \S~\ref{sec:min-rep-sets}, which formalize the idea that polyhedral losses ``behave like'' discrete losses.
In particular, any polyhedral loss $L$ has a finite \emph{representative set} $\Sc$ of reports, such that for all distributions, some report in $\Sc$ is $L$-optimal.
We show that $L$ embeds the discrete loss $\ell = L|_\Sc$ given by restricting $L$ to just the reports in $\Sc$.
To go from a discrete loss to a polyhedral one, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.

@@

We now define an embedding, which is a special case of indirect property elicitation.
(This fact is non-trivial; see Lemma~\ref{lem:embed-implies-indirect-elic}.)\jessiet{Flag; empty reference now}
In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
\begin{definition}[Embedding]\label{def:loss-embed}
  A minimizable loss $L:\reals^d\to\reals^\Y_+$ \emph{embeds} a loss $\ell:\R\to\reals^\Y_+$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that an embedding is not \emph{necessary} for these conditions.  
For example, while logistic loss does not embed 0-1 loss, logistic loss and the sign link are still consistent for 0-1 loss.
However, we show in \S~\ref{sec:poly-ie-consistency} that (minimizable) polyhedral indirect elicitation implies the existence of a calibrated link, and we leverage the fact that every polyhedral surrogate embeds a discrete loss as an intermediary step in the proof.
%However, when restricting to (minimizable) polyhedral surrogates, embedding is necessary and sufficient for calibration, which we show in \S~\ref{sec:poly-ie-consistency}.
\raft{In what sense is this last sentence true?  That section is saying $L$ indirectly elicits $\ell$ $\implies$ $L$ (with some link, maybe a different one) is consistent for $\ell$.  Agreed it would be nice to say something about that here.}
\jessiet{Thanks for catching that-- updated the sentence to be accurate, but I'm not actually sure if we want it here.  Feel free to delete if there isn't a smooth was to fit it in.}
\raft{TODO: Loop back}

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}.
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \cite{abernethy2013efficient} and in connections between proper losses and mechanism design \cite{frongillo2014general}.

@@

The key idea behind our construction is a restatement of calibration\jessiet{for a calibrated link vs calibrated surrogate-link pair?} equivalent for discrete prediction problems, to a condition we call \emph{separation}.
Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.
We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.

@@

To prove Theorem \ref{thm:link-main}, \jessie{which states that embedding implies calibration}, we now show how to construct a calibrated link from an embedding.
In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
See \S~\ref{app:sep-link-exists} for the proof.
\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$ produces a nonempty set of links, all of which are $\epsilon$-separated with respect to $L$ and $\ell$.
\end{restatable}

@@

For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
The first step of the proof is to show that this scenario cannot arise.
\begin{equation}
  \label{eq:intersection-property-embedding}
  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_u \neq \emptyset~.
\end{equation}
\jessiet{typo? $R_U$?}
\noindent
Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
(Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)

@@

\begin{figure}
	\begin{minipage}{0.29\linewidth}
    \input{tikz/abstain-intuition}
\end{minipage}
\begin{minipage}{0.71\linewidth}
	\caption{Using an embedding to show inconsistency.
    Let $L$ be a surrogate and $\ell$ a desired target; here $L=\BEP$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
    Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$ be the properties elicited by these losses; here $\gamma = \mode$, as 0-1 loss elicits the mode.
    The level sets of $\Gamma$ are given in solid black lines, and those of $\gamma$ in dashed blue lines.
    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\Gamma_u$ (here $u=0$ for $\BEP$) but in different cells of $\gamma$.
    These distributions will satisfy $\Gamma(p) = \Gamma(p')$ but $\gamma(p) \neq \gamma(p')$.
    Hence, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be equal to $\gamma(p)$ and $\gamma(p')$ simultaneously.
    In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, it will be $\ell$-suboptimal for at least one, violating calibration.
    We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
    For this example, the $\BEP$ is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
	}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}

@@

%% giving intuition for abstain figure: how to use fig to find consistency restrictions
As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
In particular, since the abstain report $\bot$ is $\ellabstain$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
\raft{I simplified this paragraph to reduce redundancy, and rewrote much of the figure caption so it's clearer how it applies more generally.  See what you think!}
\jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.  I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...}
% , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$. 
% As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
% The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.

@@

\subsection{Embedding ordered partitions via Weston-Watkins hinge}
\label{sec:winge}
As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting included a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution, \citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
\LWW(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.
\end{equation}
This surrogate $\LWW$ was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.\raft{FYI: changed notation to match the style of our other surrogates.  Not sure I care enough to change the top-$k$ ones though... \jessie{Changed the macro for top-$k$... was that what you meant?}}

@@

For example, one of the surrogates is $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$.
The authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which are tighter than previous constraints~\citep{yang2018consistency}.
\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK? \jessie{Exactly; burn}}

@@

  Consider $\psi := \psi^\R \circ \hat\psi$ and fix $p\in\simplex$.
	For any $u\in\reals^d$, if $\hat\psi(u) \in \hat\gamma(p)$, then $\psi(u) = \psi^\R\circ \hat\psi(u) \in \gamma(p)$ by definition of $\hat\psi$ and $\psi^\R$.
  Contrapositively\raft{You heard me},
  $\psi(u) \notin \gamma(p) \implies \hat\psi(u) \notin \hat\gamma(p)$.
  Thus, we have
  \begin{equation*}
    \label{eq:link-set-inclusion}
    \{u\in\reals^d \mid \psi(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \hat\psi(u) \not \in \hat\gamma(p) \}~.
  \end{equation*}
  Combined with the fact that $(L,\hat\psi)$ is calibrated with respect to $\hat\ell$, we have
	\begin{align*}
\inf_{u\in\reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} \geq	\inf_{u\in\reals^d : \hat\psi(u) \not \in \hat\gamma(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}~,
	\end{align*}
  showing calibration of $\psi$.
	%Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}.
\end{proof}

@@

  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
  \raft{Could write $\beta$ explicitly; it's in my notes}
  Thus, for all $j\in J$, we have
  \begin{align*}
    d_\infty(u_i,\Gamma(p)) < \epsilon_j
    &\implies \exists u^*\in\Gamma(p)\; \|u_j-u^*\|_\infty < \epsilon_j
    \\
    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| < \beta\epsilon_j
    \\
    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| < \beta\epsilon_j~.
  \end{align*}
  Finally, for this $p$, we have
  \begin{align*}
    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
    \leq
    \inf_{j\in J} \inprod{p}{L(u_j)}
    =
    \risk{L}(p)~,
  \end{align*}
  contradicting the calibration of $\psi$.
\end{proof}

@@

	It remains to show (iii).
	Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
	It suffices to show that, (a) for each facet $F$ of $P$, there is an $H^+ \in \H$ such that $F = H\cap P$, and (b) if $F$ is a facet of $P$ and $H,H'$ are hyperplanes with $F = H \cap P = H' \cap P$, then it must be the case that $H = H'$.
	For (a), \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
	Moreover, the hyperplanes defining facets are unique, as noted in the last sentence of the proof of \citep[Proposition 4.5]{gallier2008notes}.
	Since $x \in \relint(F)$ is in exactly one face of $F$, namely $F$ itself, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
	For (b), consider that if $F$ is a facet of $P$, which is $d$-dimensional, its affine hull is a hyperplane in $\reals^d$.
	As hyperplanes are uniquely defined, it must be the case that $H = H'$.
%  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
%  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
%  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
%  Therefore, we must have $H^+ \in \H$ as well.

>>>>

\newcommand{\Li}[1]{L^{(#1)}}
\newcommand{\Ri}[1]{\R^{(#1)}}
\newcommand{\elli}[1]{\ell^{(#1)}}

@@

%% intuition for the relationship between polyhedral surrogates and discrete target losses
Underpinning our results are several observations, outlined in \S~\ref{sec:min-rep-sets}, which formalize the idea that polyhedral losses ``behave like'' discrete losses.
In particular, any polyhedral loss $L$ has a finite \emph{representative set} $\Sc$ of reports, such that for all distributions, some report in $\Sc$ is $L$-optimal.
We show that $L$ embeds the discrete loss $\ell = L|_\Sc$ given by restricting $L$ to just the reports in $\Sc$.
To go from a discrete loss to a polyhedral surrogate, we prove that the conditions of an embedding are equivalent to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}), and use the fact that discrete losses and polyhedral losses both have polyhedral Bayes risks.

@@

We now define an embedding, which is a special case of indirect property elicitation.
(This fact is non-trivial; see Lemma~\ref{lem:embedding-implies-indirect-elic}.)
In addition to matching loss values, as described above, we require the original reports to be $\ell$-optimal exactly when the corresponding embedded points are $L$-optimal.
\begin{definition}[Embedding]\label{def:loss-embed}
  A minimizable loss $L:\reals^d\to\reals^\Y_+$ \emph{embeds} a loss $\ell:\R\to\reals^\Y_+$ if there exists a representative set $\Sc$ for $\ell$ and an injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\Sc$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  If $\Sc$ is a minimal representative set, we say $L$ \emph{tightly embeds} $\ell$.
  %if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

While our notion of embedding is sufficient for calibration (and therefore consistency), it is worth noting that an embedding is not \emph{necessary} for these conditions.  
For example, while logistic loss does not embed 0-1 loss, logistic loss and the sign link are still consistent for 0-1 loss.
When working with polyhedral surrogates, however, embeddings are necessary for calibration in a strong sense, as we discuss in \S~\ref{sec:poly-ie-consistency}: if a polyhedral surrogate $L$ has a calibrated link to some target $\ell$, then $L$ must embed some discrete target $\hat\ell$ which can then be linked to $\ell$.

@@

The proof of Theorem~\ref{thm:discrete-loss-poly-embeddable} uses a construction via convex conjugate duality similar to many constructions in the literature. 
%(e.g.\ \cite{duchi2018multiclass,abernethy2013efficient,frongillo2014general}).
For example, the literature on minimax optimization in supervised learning settings \citep{asif2015adversarial,farnia2016minimax,fathony2016adversarial} poses a minimax optimization problem of the expected loss matrix over both players' strategies, which becomes a convex relaxation of the discrete optimization problem\raft{We said ``poses the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable}'' -- is it exactly the same?  We just have to say how it relates, like ``when viewing X as Y, one arrives at the same construction'', or maybe one is a special case of the other.}\raf{Update 6/12/2022: looks like this sentence changed, but now isn't tied to Theorem~\ref{thm:discrete-loss-poly-embeddable}...}.
\citet{reid2012convexity} construct a canonical link function for proper losses with differentiable Bayes risks; the link maps a report $p\in\simplex$ to the gradient of the Bayes risk at $p$, which uses the same duality as above.
\citet[Proposition 3]{duchi2018multiclass} give essentially the same construction as ours, but only comment on the calibration of surrogates under such constructions for multiclass classification tasks given by strictly concave losses, excluding polyhedral surrogates.
Finally, a similar construction also appears in the design of prediction markets \cite{abernethy2013efficient} and in connections between proper losses and mechanism design \cite{frongillo2014general}.

@@

The key idea behind our construction is the notion of \emph{separation}, a condition which is equivalent to calibration for discrete prediction problems.
Roughly, given a surrogate $L$ and discrete target $\ell$, a link is $\epsilon$-separated if the distance between any $L$-optimal point in $\reals^d$, and any point that links to an $\ell$-suboptimal report, is at least $\epsilon$.
\raft{Changed; previous statement was not correct I think: ``Roughly, a link is $\epsilon$-separated if the distance between any point in $\reals^d$ that links to an $\ell$-optimal report, and any point that links to a non-optimal report, is at least $\epsilon$.''}
We also show how this characterization also leads to linear \emph{regret transfer} or \emph{surrogate regret} bounds.

@@

To prove Theorem \ref{thm:link-main}, that embedding implies calibration, we now show how to construct a calibrated link from an embedding.
In light of Theorem~\ref{thm:calibrated-separated}, it now suffices to show that for any polyhedral $L$ embedding some $\ell$, there exists a \emph{separated} link $\psi$ with respect to $L$ and $\ell$.
Construction~\ref{const:eps-thick-link}, discussed next, ``thickens'' a given embedding to produce a link.
Theorem \ref{thm:thickened-separated} states that, for a small enough choice of $\epsilon$, that link is separated.
See \S~\ref{app:sep-link-exists} for the proof.
\begin{restatable}{theorem}{thickenedseparated} \label{thm:thickened-separated}
  Let polyhedral surrogate $L:\reals^d \to \reals^\Y_+$ embed the discrete loss $\ell:\R\to\reals^\Y_+$.
  Then there exists $\epsilon_0 > 0$ such that, for all $0 < \epsilon \leq \epsilon_0$, Construction~\ref{const:eps-thick-link} for $L,\ell,\epsilon,\|\cdot\|$ produces a nonempty set of links, all of which are $\epsilon$-separated with respect to $L$ and $\ell$.
\end{restatable}

@@

For (i), given the embedding $\varphi: \Sc\to\reals^d$, begin by linking each embedding point back to its original report, so that $\psi(\varphi(r)) = r$.
Now we wish to determine $\psi(u)$ for non-embedding points $u\in\reals^d$ which optimize $L$ for some distribution.
Let $\Gamma = \prop L$ and define $\U = \{\Gamma(p) \mid p\in\simplex\}$ to be the ``range'' of $\Gamma$, i.e., all possible optimal sets.
For each $U\in\U$, we can define $R_U = \{ r\in\Sc \mid \varphi(r) \in U\}$ to be the set of target reports which, by definition of embedding, are $\ell$-optimal when $U$ is $L$-optimal.
We would like to restrict $\psi(U) \subseteq R_U$, so that optimal surrogate reports are mapped to optimal target reports.
The challenge is that we could have a point $u\in U\cap U'$ for two optimal sets $U,U'\in\U$, and \emph{a priori}, it could be that $R_U \cap R_{U'} = \emptyset$.
The first step of the proof is to show that this scenario cannot arise.
\begin{equation}
  \label{eq:intersection-property-embedding}
  \forall \U'\subseteq\U, \; \cap_{U\in\U'} U \neq \emptyset \implies \cap_{U\in\U'} R_U \neq \emptyset~.
\end{equation}
\noindent
Thus, for any $u\in\cup\U$, we have a nonempty set of valid choices for $\psi(u)$.
(Eq.~\eqref{eq:intersection-property-embedding} may appear similar to indirect elicitation; in fact the two conditions are equivalent, as we discuss in \S~\ref{sec:poly-ie-consistency}.)

@@

\begin{figure}
	\begin{minipage}{0.28\linewidth}
    \input{tikz/abstain-intuition}
\end{minipage}
\begin{minipage}{0.72\linewidth}
	\caption{Using an embedding to show inconsistency.
    Let $L$ be a surrogate embedding $\ell$, and let $\ell$ be a desired target; here $L=\BEP$, $\hat\ell = \ellabstain$ (\S~\ref{sec:abstain}) and $\ell$ is 0-1 loss for multiclass classification.
    Let $\Gamma = \prop{L}$, $\hat\gamma = \prop{\hat\ell}$, and $\gamma = \prop{\ell}$ be the properties elicited by these losses; here $\gamma = \mode$, as 0-1 loss elicits the mode.
    The level sets of $\hat\gamma$ are given in solid black lines, and those of $\gamma$ in dashed blue lines.
    To exhibit non-calibration, take distributions $p, p'$ in the relative interior of the blue cell $\gamma_{\hat r}$ (here $\hat r=\bot$ for $\ellabstain$) but in different cells of $\gamma$.
    These distributions will satisfy $\hat\gamma(p) = \hat\gamma(p')$, and thus $\Gamma(p) = \Gamma(p')$ by definition of embedding, but $\gamma(p) \cap \gamma(p') = \emptyset$.
    Taking $u\in\Gamma(p)=\Gamma(p')$, it is impossible to define $\psi(u)$ to satisfy calibration, as $\psi(u)$ cannot be in $\gamma(p)$ and $\gamma(p')$ simultaneously.
    In particular, even though $u$ is $L$-optimal for both $p$ and $p'$, $\psi(u)$ will be $\ell$-suboptimal for at least one, violating calibration.
    We may impose restrictions on the conditional label distributions to remove the blue cell, however, and thus satisfy calibration.
    For this example, the $\BEP$ is classification-calibrated if one restricts to the set of distributions where at least one label $y\in\Y$ has probability $p_y \geq \tfrac 1 2$.
	}
	\label{fig:abstain-intuition-inconsistent}
	\end{minipage}
\end{figure}

@@

%% giving intuition for abstain figure: how to use fig to find consistency restrictions
As an illustration, one can use the fact that $\BEP$ embeds $\ellabstain$ to verify that $\BEP$ is inconsistent for multiclass classification, i.e., with respect to 0-1 loss.
In particular, since the abstain report $\bot$ is $\ellabstain$-optimal whenever $\max_{y\in\Y} p_y \leq 1/2$, by the definition of embedding, the origin $0\in\reals^d$ is $\BEP$-optimal for the same distributions.
Recalling that 0-1 loss elicits the mode, one can now find two distributions with different modes but for which $0$ is $\BEP$-optimal, violating calibration (Figure~\ref{fig:abstain-intuition-inconsistent}).
\raft{I simplified this paragraph to reduce redundancy, and rewrote much of the figure caption so it's clearer how it applies more generally.  See what you think!}
\jessiet{I really like the caption now, but in the caption we're comparing $\prop{L}$ to $\prop{\ell}$ and in the paragraph we mention $\prop{\hat \ell}$, where $\hat \ell$ is the embedded loss.  I kinda like working through $\prop{\hat\ell}$ since it justifies this framework a bit more, but also the drawings look the exact same for $\BEP$ and $\ellabstain$...}
\raft{Good call -- that was the whole point after all!  I updated to include the embedded property.}
% , one can observe that the BEP surrogate $\BEP$ does not indirectly elicit the mode, as the level sets $\Gamma_{\vec 0} = \hat \gamma_\bot$ are equal by the definition of embedding, yet one can observe $\prop{\ellabstain}_\bot \not \subseteq \mode_r$ for any $r$. 
% As embedding is a special form of indirect elicitation, we additionally know the BEP surrogate does not embed the mode.
% The intuition described by Figure~\ref{fig:abstain-intuition-inconsistent} additionally gives a procedure to validate (in)consistency with respect to a target task.

@@

\subsection{Embedding ordered partitions via Weston-Watkins hinge}
\label{sec:winge}
As the hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting included a one-vs-all reduction to the binary problem via hinge loss, generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution, \citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
\LWW(u)_y = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.
\end{equation}
This surrogate $\LWW$ was later shown to be inconsistent with respect to 0-1 loss~\citep{tewari2007consistency,liu2007fisher}.

@@

For example, one of the surrogates is $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$.
The authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
Using the losses each proposed surrogate embeds, using the same technique from Figure~\ref{fig:abstain-intuition-inconsistent}, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification; these constraints are tighter than previous constraints~\citep{yang2018consistency}.

@@

  Consider $\psi := \psi^\R \circ \hat\psi$ and fix $p\in\simplex$.
	For any $u\in\reals^d$, if $\hat\psi(u) \in \hat\gamma(p)$, then $\psi(u) = \psi^\R\circ \hat\psi(u) \in \gamma(p)$ by definition of $\hat\psi$ and $\psi^\R$.
  Contrapositively\btw{You heard me},
  $\psi(u) \notin \gamma(p) \implies \hat\psi(u) \notin \hat\gamma(p)$.
  Thus, we have
  \begin{equation*}
    \label{eq:link-set-inclusion}
    \{u\in\reals^d \mid \psi(u) \not \in \gamma(p) \} \subseteq \{u\in\reals^d \mid \hat\psi(u) \not \in \hat\gamma(p) \}~.
  \end{equation*}
  Combined with the fact that $(L,\hat\psi)$ is calibrated with respect to $\hat\ell$, we have
	\begin{align*}
\inf_{u\in\reals^d : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)} \geq	\inf_{u\in\reals^d : \hat\psi(u) \not \in \hat\gamma(p)} \inprod{p}{L(u)} > \inf_{u\in\reals^d}\inprod{p}{L(u)}~,
	\end{align*}
  showing calibration of $\psi$.
	%Consistency follows as calibration and consistency are equivalent in this setting~\citep{ramaswamy2016convex}.
\end{proof}

@@

  Next, observe that, as $L$ is polyhedral, the expected loss $\inprod{p}{L(u)}$ is $\beta$-Lipschitz in $\|\cdot\|_\infty$ for some $\beta>0$.
  \btw{RF: Could write $\beta$ explicitly; it's in my notes}
  Thus, for all $j\in J$, we have
  \begin{align*}
    d_\infty(u_i,\Gamma(p)) < \epsilon_j
    &\implies \exists u^*\in\Gamma(p)\; \|u_j-u^*\|_\infty < \epsilon_j
    \\
    &\implies \left| \inprod{p}{L(u_j)} - \inprod{p}{L(u^*)} \right| < \beta\epsilon_j
    \\
    &\implies \left| \inprod{p}{L(u_j)} - \risk{L}(p) \right| < \beta\epsilon_j~.
  \end{align*}
  Finally, for this $p$, we have
  \begin{align*}
    \inf_{u:\psi(u)\notin\gamma(p)} \inprod{p}{L(u)}
    \leq
    \inf_{j\in J} \inprod{p}{L(u_j)}
    =
    \risk{L}(p)~,
  \end{align*}
  contradicting the calibration of $\psi$.
\end{proof}

@@

	It remains to show (iii).
	Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
  As noted in the last sentence of the proof of \citep[Proposition 4.5]{gallier2008notes},
  the hyperplanes defining facets are unique:
  if $F$ is a facet of $P$ and $H,H'$ are hyperplanes with $F = H \cap P = H' \cap P$, then it must be the case that $H = H'$.
	It therefore suffices to show that, for each facet $F$ of $P$, there is an $H^+ \in \H$ such that $F = H\cap P$.
  \citet[Proposition 3.17]{gallier2008notes} observes that, for all $x \in \partial P$, there exists some hyperplane $\hat H$ such that $\hat H$ supports $P$ at $x$.
	Since $x \in \relint(F)$ is in exactly one face of $F$, namely $F$ itself, there must be a unique $H^+ \in \H$ such that $F = H \cap P$.
%  Let $\H$ be a finite set of closed halfspaces such that $P = \cap \H$.
%  By (ii), each $H^+ \in \H^*$  determines a facet of $P$.
%  If $H^+ \not \in \H$, then $\cap \H \neq P$ as convex polytopes are uniquely determined by their facets (cf.~\citep[pg. 455]{schneider2014convex})\raft{This citation is doing the heavy lifting---what exactly does it say?}, a contradiction.
%  Therefore, we must have $H^+ \in \H$ as well.
\end{proof}
